Behavior Driven Development in Haskell

### 2012-05-25 paper.tex
adding note.
rephrasing parameter.

\begin{description}
\item[developer] programmers who develop libraries
\item[users] programmers who use libraries
%%\item[unit test] tests for individual programs or libraries.
\item[example] Typical usage of functions.
\item[property] Invariants which functions have.
\item[behavior] How do functions behave for users. Behavior can be shown by using both examples and properties.
\item[documentation] Explanation of functions.
\end{description}

@@

To specify properties, we also propose a new markup. In this paper, we use the {\tt prop>} prefix. We can write the no-parameter equation as follows:

@@

\noindent Of course, we allowed parameterized properties by
using closed lambda terms.
Type signatures can be specified for each parameter:

@@

Since no-parameter properties have no parameters,
it is enough to test them just one.
However, QuickCheck 2.3 or earlier tests no-parameter properties 100 times.
More precisely, the evaluation results are memorized and they are
compared with {\tt True} 100 times.
The current maintainer of QuickCheck modified so that
no-parameter properties are tested just once in its source repository.
This feature will be available in the future release.

@@

@@

We are grateful to David Waern, 
one of the Haddock maintainers, 
for reviewing two new markups to Haddock.
We would like to thank
Nick Smallbone for having improved QuickCheck so that no-parameter properties are tested just once.

>>>>

\begin{description}
\item[developer] programmers who develop libraries
\item[users] programmers who use libraries
%%\item[unit test] tests for individual programs or libraries.
\item[example] Typical usage of functions. (TBD(@sol): more vocal)
\item[property] Invariants which functions have.
\item[behavior] How do functions behave for users. Behavior can be shown by using both examples and properties.
\item[documentation] Explanation of functions.
\end{description}

@@

To specify properties, we also propose a new markup. In this paper, we use the {\tt prop>} prefix. We can write properties which do not take parameters as follows:

@@

\noindent Of course, we allowed properties which take parameters by
using closed lambda terms.
Type signatures can be specified for each parameter:

@@

It is enough to test properties which do not have parameters just one.
However, QuickCheck 2.3 or earlier tests 
properties which do not have parameters 100 times.
More precisely, the evaluation results are memorized and they are
compared with {\tt True} 100 times.
The current maintainer of QuickCheck modified so that
properties which do not have parameters
are tested just once in its source repository.
This feature will be available in the future release.

@@

\begin{quote}
    \emph{should emphasize ``automatically discover tests''}
\end{quote}

\begin{quote}
    \emph{talk about CI}
\end{quote}

@@

We are grateful to David Waern, 
one of the Haddock maintainers, 
for reviewing two new markups to Haddock.
We would like to thank
Nick Smallbone for having improved QuickCheck so that 
properties which do not have parameters are tested just once.
